Geometrization of characters of smooth group schemes over finite fields\\ with an application to types for supercuspidal representations

### 2016-03-03 followup.tex
Arguable improvements to notation: back to Q. Typos.

Now suppose $q : G \to G_0$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G_0.
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
Consider the functor
\[
q^* : \CS(G_0) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}[column sep=40]
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
& p^* (q^*\cs{L}_0)
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(G_0) \to CS_H(G)
\]
and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
\begin{equation}\label{qH}
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G_0) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\end{equation}
The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.

\begin{lemma}\label{lem:torsor}
If $q : G \to G_0$ is an $H$-torsor in the fpqc topology 
then $q_H^*: \CS(G_0) \to \CS_H(G)$ is an equivalence.
\end{lemma}

\begin{proof}
First we observe that the comparison functor 
$\Loc(G_0) \to \Loc_H(G)$ is an equivalence.
To see this, first recall that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms of affine schemes over $\Fq$.
It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fpqc topology; see \cite{Vistoli:notes}*{Lem 4.25} for example.
(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fpqc topology; see \cite{Vistoli:notes}*{Thm 4.23} for example.)
Since $q : G\to G_0$ is an $H$-torsor in the fpqc topology, is now follows from descent theory that the comparison functor $\Loc(G_0) \to \Loc_H(G)$ is an equivalence; see \cite{Vistoli:notes}*{Thm 4.46} for example.)
%\todo{Need more specific references}

For use below, we write $L_1 : \Loc(G_0) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to \Loc(G_0)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
%
Arguing as above, we also see that pull-back along $q\times q$ determines an equivalence $L_2 : \Loc(G_0\times G_0) \to \Loc_{H\times H}(G\times G)$.
For use below, we write $R_2 : \Loc_{H\times H}(G\times G) \to \Loc(G_0\times G_0)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.

We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$:
on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$; on maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
Direct calculation confirms \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}, and therefore that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$; 
likewise, $L_1(\alpha_0)$ is a map in $\CS_H(G)$ after checking \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
%
With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
The adjunction is built from the adjunctions $(\epsilon_1, \eta_1)$ and $(\epsilon_2, \eta_2)$ for $(L_1,R_1)$ and $(L_2, R_2)$.
\end{proof}

@@

It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil} that there is a Weil sheaf $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
\begin{equation}
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\end{equation}
%
Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.

First, fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
One begins by finding a local system $\cs{K}_0$ on $S_0 \times V^\sharp$ such that 
\[
\trFrob{\cs{K}_0[2\dim V](\dim V)} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
\]
where $\cs{K}_0[2\dim V](\dim V)$ is the Tate twist of the shift of $\cs{K}_0$.
This is done by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that 
\begin{equation}\label{Cayley}
\trace(W_\psi)(g,v,z) =  q^{-\dim V} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi(\langle \cay(g)v,v\rangle) \psi(z),
\end{equation}
 for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
By a simple adaptation of what in \cite{Gurevich-Hadani:geometric_Weil}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible local system $\cs{K}_0$ on $S_0 \times V^\sharp$. 
Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$. 
It follows from \cite{Gurevich-Hadani:geometric_Weil} that 
\[
\trFrob{\cs{K}[\dim V](\dim V)} = \trace(W_\psi).
\]
Then $\cs{W}_\psi = \cs{K}[\dim V](\dim V)$ is the promised Weil sheaf.

@@

As a step toward geometrizing the type $(C,\rho)$, we now recall some results from \cite{yu:03a}.

@@

Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following provocative observation, which we have just revisited.
\begin{quotation}
{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
\end{quotation}
%In fact, Yu's description of how to assemble $\rho$ from $(\rho^0, \varphi^0, \ldots , \varphi^d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.

@@

\begin{proposition}\label{prop:geotypes}
Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
Let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:models}.
Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Then there is a virtual Weil sheaf $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
\end{proposition}

@@

By \cite{lusztig:disconnected1}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \varrho_0^\reductive.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \varrho_0.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}. 
With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to G_0^0$.
Factor
\[
\begin{tikzcd}
G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE \\
& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\rho_0)_m} 
\end{tikzcd}
\]
Observe that $\trace(\rho_0)_m$ may be recovered from ${A}_m^0$:
\[
\trFrob{{A}^0_m} = \trace(\rho_0)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.

>>>>

Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
Q.
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $Q$.
Consider the functor
\[
q^* : \CS(Q) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}[column sep=40]
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
& p^* (q^*\cs{L}_0)
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(Q) \to CS_H(G)
\]
and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
\begin{equation}\label{qH}
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(Q) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\end{equation}
The definition of $q_H^* : \CS(Q)\to \CS_H(G)$ will be revisited in the proof of the following result.

\begin{lemma}\label{lem:torsor}
If $q : G \to Q$ is an $H$-torsor in the fpqc topology 
then $q_H^*: \CS(Q) \to \CS_H(G)$ is an equivalence.
\end{lemma}

\begin{proof}
%First we observe that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence.
%To see this, first recall that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
%Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms of affine schemes over $\Fq$.
%It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fpqc topology; see \cite{Vistoli:notes}*{Lem 4.25} for example.
%(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fpqc topology; see \cite{Vistoli:notes}*{Thm 4.23} for example.)
Since $q : G\to Q$ is an $H$-torsor in the fpqc topology, is follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence; see \cite{Vistoli:notes}*{Thm 4.46} for example.)
%
For use below, we write $L_1 : \Loc(Q) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to \Loc(Q)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
%
Arguing as above, we also see that pull-back along $q\times q$ determines an equivalence $L_2 : \Loc(Q\times Q) \to \Loc_{H\times H}(G\times G)$.
For use below, we write $R_2 : \Loc_{H\times H}(G\times G) \to \Loc(Q\times Q)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.

We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$:
on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$; on maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
Direct calculation confirms \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}, and therefore that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$; 
likewise, $L_1(\alpha_0)$ is a map in $\CS_H(G)$ after checking \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
%
With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
The adjunction is built from the adjunctions $(\epsilon_1, \eta_1)$ and $(\epsilon_2, \eta_2)$ for $(L_1,R_1)$ and $(L_2, R_2)$.
\end{proof}

@@

It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil} that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
\begin{equation}
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\end{equation}
%
Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.

Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
One begins by finding a local system $\cs{K}_0$ on $S_0 \times V^\sharp$ such that 
\[
\trFrob{\cs{K}_0[2\dim V](\dim V)} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
\]
where $\cs{K}_0[2\dim V](\dim V)$ is the Tate twist of the shift of $\cs{K}_0$.
This is done by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that 
\begin{equation}\label{Cayley}
\trace(W_\psi)(g,v,z) =  q^{-\dim V} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi(\langle \cay(g)v,v\rangle) \psi(z),
\end{equation}
 for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
By a simple adaptation of what in \cite{Gurevich-Hadani:geometric_Weil}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ on $S_0 \times V^\sharp$. 
Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$. 
It follows from \cite{Gurevich-Hadani:geometric_Weil} that 
\[
\trFrob{\cs{K}[\dim V](\dim V)} = \trace(W_\psi).
\]
Then $\cs{W}_\psi = \cs{K}[\dim V](\dim V)$ is the promised Weil sheaf complex.

@@

Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
\begin{quotation}
{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
\end{quotation}
In this section we explain what this observation is saying, following \cite{yu:03a}.

@@

@@

\begin{proposition}\label{prop:geotypes}
Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
Let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:models}.
Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Then there is a virtual Weil sheaf complex $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
\end{proposition}

@@

By \cite{lusztig:disconnected1}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \varrho_0^\reductive.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \varrho_0.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $Q^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}. 
With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to Q^0$.
Factor
\[
\begin{tikzcd}
G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE \\
& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\rho_0)_m} 
\end{tikzcd}
\]
Observe that $\trace(\rho_0)_m$ may be recovered from ${A}_m^0$:
\[
\trFrob{{A}^0_m} = \trace(\rho_0)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
